---
title: "DDP_Assignment_week4"
author: "Alex Perez Nava"
date: "10/7/2019"
output: ioslides_presentation
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

##  Executive Summary

There is a set of variables related to miles per gallon (MPG) (outcome). Here the difference of the MPG between automatic and manual transmissions is the center of the analysis. 
The mtcars dataset  is the data source. Regression models function is used to solve the following two questions:

* “Is an automatic or manual transmission better for MPG?”
*  “Quantifying how different is the MPG between automatic and manual transmissions?”

## Load and Test Data
The data was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973–74 models).

```{r cache=TRUE}
library(datasets)
mpgData <- with(mtcars, data.frame(mpg, am))
mpgData$am <- factor(mpgData$am, labels = c("Automatic", "Manual"))
summary(mpgData)
```

## Is an automatic or manual transmission better for MPG?

```{r cache=TRUE}
summary(mpgData[mpgData$am == "Automatic",])
summary(mpgData[mpgData$am == "Manual",])
```

## Quantifying how different is the MPG between automatic and manual transmissions? 

```{r cache=TRUE}
fit <- lm(mpg ~ as.integer(am), data=mpgData)
summary(fit)
```

# Results
So, manual transmission is better than automatic for MPG, which increased by `r coef(fit)[2]`.

# Appendix

## Fig 1. MPG between automatic and manual transmissions

```{r cache=TRUE}
par(mfrow=c(1,2))
with(mpgData,{
     boxplot(mpg ~ am, 
             ylab = "miles per gallon (MPG)")
     plot(mpg ~ as.integer(am),
             xlab = "Automatic (1) or Manual(2)",
             ylab = "miles per gallon (MPG)")
     abline(fit, col=2)
     })
```
